---
title: "ESM204-Assignment3"
author: "Geoffrey Cook & Tara Jagadeesh"
date: "5/16/2019"
output:
  html_document: default
  pdf_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r Reading in Libraries and Databases, include=FALSE}
##############################################################
# Reading in libraries and databases
##############################################################

# Libraries
library(tidyverse)
library(car)
library(RColorBrewer)
library(stargazer)
library(vcdExtra)
library(reshape2)
library(effsize)
library(pwr)
library(kableExtra)
library(corrplot) 
library(janitor)
library(lubridate) 
library(gganimate)
library(ggimage)
library(plotly)
library(knitr)

# Data
whales <- read_csv("HW3Data.csv")

```

```{r Question 1, results='asis', messages=FALSE, include=TRUE}
##############################################################
# Question 1
##############################################################
# Create a linear probability model that predicts a respondent’s probability of voting ‘yes’ on the ballot based on their age, income, NEP score, the risk reduction offered by the program, and the cost of the program to that respondent. Show the model and interpret the regression coefficients
##############################################################

# Probability of voting 'YES'
### Not sure if all we need to have here are the coefficients but if so, this seems to give those to us.

p_yes <- lm(vote ~ age+income+NEP+risk+bid, data = whales)
summary(p_yes)

# Making a table for the linear model results
table_p_yes <- stargazer(p_yes)

```
1. Create a linear probability model that predicts a respondent’s probability of voting ‘yes’ on the ballot based on their age, income, NEP score, the risk reduction offered by the program, and the cost of the program to that respondent. Show the model and interpret the regression coefficients

The following is the linear regression equation:
Y_yes = 0.1196977 + (0.0099816*agetofifty) + (-0.0201190*agetoforty) + (-0.0162261*agetosixty) + (0.0204401*agetothirty) + (0.0088282*incomeone_percent) + (0.0027386*incomepoor) + (0.0074891*incomerich) + (0.0467922*incomevery_rich) + (0.0158639*NEP) + (0.0007445*risk) + (-0.0010699*bid)

```{r Question 2, results='asis', messages=FALSE, include=FALSE}
##############################################################
# Question 2
##############################################################
# Based on this regression, what can you say about the value of a single prevented whale death? (Hint: Think about how risk reduction for all whales translates into the number of whale deaths avoided)
##############################################################

value_per_whale <- -4*(p_yes$coefficients["risk"]/p_yes$coefficients["bid"])
# value_per_whale = $2.7834

```
2.  Based on this regression, what can you say about the value of a single prevented whale death? (Hint: Think about how risk reduction for all whales translates into the number of whale deaths avoided

Based on this equation, assuming a 20% reduction in whale strike likelihood saves 5 whales, the value of each whale saved under this assumption is approximately $2.78.

```{r Question 3, results='asis', messages=FALSE, include=FALSE}
##############################################################
# Question 3
##############################################################
# Pick three arbitrary respondents. For each of those respondents, estimate their WTP for a VSR program offering 60% risk reduction
##############################################################

# Create a sub data frame that only includes risk = 60 in their column
risk_60 <- whales %>% 
  filter(risk == "60")

# From that new list, select three random respondants and determine their respective WTP (bid)
##################################
# Row: 6
# Risk = 60
# NEP = 24
# Income = one_percent
# Age = tothirty
##################################

bid_person1 = (0.5 - 0.1196977 - (0.0204401*1) - (0.0088282*1) - (0.0158639*24) - (0.0007445*60)) / (-0.0010699)
# bid_person1 = 69.5107954014394

##################################
# Row: 16
# Risk = 60
# NEP = 27
# Income = poor 
# Age = tofifty
##################################

bid_person2 = (0.5 - 0.1196977 - (0.0099816*1) - (0.0027386*1) - (0.0158639*27) - (0.0007445*60)) / (-0.0010699)
# bid_person2 = 98.5262174034957

##################################
# Row: 65
# Risk = 60
# NEP = 45
# Income + very_rich
# Age = oversixty
##################################

bid_person3 = (0.5 - 0.1196977 - (-0.0201190*1) - (0.0467922*1) - (0.0158639*40) - (0.0007445*60)) / (-0.0010699)
# bid_person3 = 304.324609776615
```

